---
title       : Brief Introduction to Pricing Derivatives
subtitle    : Pricing a Call Option with a Two Step Binomial Model
author      : Robby Twesten & Tristan McDougall 
job         : RT Financials
framework   : io2012     # {io2012, html5slides, shower, dzslides, ...}
highlighter : highlight.js  # {highlight.js, prettify, highlight}
hitheme     : tomorrow      # 
widgets     : [mathjax, bootstrap]            # {mathjax, quiz, bootstrap}
mode        : selfcontained # {standalone, draft}
knit        : slidify::knit2slides
---

## Outline
### Tools:  
1. Programming Environment
2. Probability
3. Calculus

### Finance Theory:  
1. Future Value of Money
2. Binomial Tree Pricing Model for Option

### Conclusions

--- .class #id

## Programming Environment

### R is a free statistical software package with integrated graphics
* [Open Source Code](http://cran.r-project.org/), Shared Libraries, & [Integrated Development Environment](http://www.rstudio.com/) 
```{r echo=FALSE, warning=FALSE, results='hide', message=FALSE}
require(stringr)
require(DiagrammeR)
require(slidify)
require(knitr)
require(ggplot2)
require(grid)
require(gridExtra)
require(gtable)
require(lubridate)
library(dplyr)
library(lubridate)
library(Cairo)
library(animation)
library(htmlwidgets)
ani.options(interval=.6)
```

* [Plotting](http://ggplot2.org/), [LaTex](http://www.latex-project.org/) for equations, & [Slide Presentations](https://github.com/ramnathv/slidifyExamples)

### Version Control
* [Git](https://www.git-scm.com) invented by Linus Torvalds (open source Linux)
* [Git Hub](https://github.com/RobertTwesten/Tristan) distributed version control ([used by Google](https://github.com/google))

---
## Tools from Calculus

### Definition of $e$

<div class="centered">
\begin{equation}
    e = \lim_{n\to\infty} (1 + 1/n)^n
\end{equation}
</div>

### Integration

* Assume a [linear measure]( http://en.wikipedia.org/wiki/Measure_(mathematics\) ) in $\Re^1$, then
\begin{equation}
    \int dx = x + C
\end{equation}

### Total Derivative

* Let $f$ be a function of $x(t)$, $y(t)$, and $t$. The total derivative with respect to time is

\begin{equation}
    \frac{d f(x(t), y(t), t)}{d t} = \frac{\partial f}{\partial x} \frac{d x}{d t} + \frac{\partial f}{\partial y} \frac{d y}{d t}
    + \frac{\partial f}{\partial t} \frac{d t}{d t}
\end{equation}

---
## Tools from Statistics

### Observations
* Given a set of observations $\{x_i\}$, the mean is

<div class="centered">
\begin{equation}
    \mu =  \sum_{i=1}^{n} \frac{x_i}{n}
\end{equation}
</div>


* The variance (a measure of disorder) is

<div class="centered">
\begin{equation}
   \sigma^2  =  \sum_{i=1}^n \frac{(x_i - \mu)^2}{n}
\end{equation}
</div>

\begin{equation}
\vdots
\end{equation}

<div class="centered">
\begin{equation}
   \sigma^2  =  E[x^2] - E[x]^2
\end{equation}
</div>

---
## Tools from Probability (1 / 3)
### [Stochastic Processes](http://en.wikipedia.org/wiki/Stochastic_process): observations whose values are random with respect to time


### Markov Process
* Future stock price depends only on current price.
* Distributions are normal. Means are additive. Variances are additive.

### Wiener Process

* Future stock price depends only on current price.
* Distributions are standard normal, i.e. $\mu = 0$ &  $\sigma^2 = 1$.

---
## Tools from Probability (2 / 3)
### Normal Distribution
* Density is
<div class="centered">
\begin{equation}
   f(x) = \frac{1}{\sqrt{2 \pi} \sigma} e^{-(x - \mu)^2/2 \sigma^2}
\end{equation}
</div>

* Shape of "bell"" curve determined by density wtih center at $\mu$ and [width](https://en.wikipedia.org/wiki/Full_width_at_half_maximum) $\propto \sigma$
* Expectation value (average) of x is

<div class="centered">
\begin{equation}
   E(x) = \langle x \rangle = \int_{-\infty}^{-\infty} x \frac{1}{\sqrt{2 \pi} \sigma} e^{-(x - \mu)^2/2 \sigma^2} dx
\end{equation}
</div>

### Standard Normal Distribution
* Definition: $\mu = 0$ &  $\sigma^2 = 1$

---
## Tools from Probability (3 / 3)
### Monte Carlo Data, Normal Distribution, & Cental Limit Theorm
* Left:  Simulated scores of 50 students with $\mu = 70$ & $\sigma = 5$
* Right:  Normalized scores of 30, 40, & 50 students $\times$ 1000 simulations

```{r CLTnrml, echo=FALSE, warning=FALSE, fig.width=12, fig.height=5}
################################################################################
##
## This code chunk initializes constants used for generating Monte Carlo data##
##
nSims = 1000
mean = 70
sd = 5 # stanard deviation for normal distributions
##
################################################################################
##
## This code chunk generates& plots Monte Carlo data for normal distribution
##
set.seed(314159)
dataNorm <- tbl_df(data.frame(x = rnorm(50, mean, sd)))
helper <- function(x) {dnorm(x, mean, sd)}
plotHistRnorm <- ggplot(dataNorm, aes(x = x)) + geom_histogram(binwidth=.3, aes(y = ..density..), colour = "black", fill = "steelblue")
plotHistRnorm <- plotHistRnorm + stat_function(fun = helper, size = 2) #+ geom_density(alpha=.2, fill="#FF6666")
plotHistRnorm <- plotHistRnorm + labs(x ="Test Score", y="Density", title = "Normal Distribution with mean = 70 and standard deviation = 5")
##
################################################################################
##
## This graph demonstrates arbitrary Normal Distribution & standardizing it
##
set.seed(314159)
rnorm30.frame <- tbl_df(data.frame(matrix(rnorm(nSims*30, mean, sd), nSims)))
set.seed(314159)
rnorm40.frame <- tbl_df(data.frame(matrix(rnorm(nSims*40, mean, sd), nSims)))
set.seed(314159)
rnorm50.frame <- tbl_df(data.frame(matrix(rnorm(nSims*50, mean, sd), nSims)))
# View(rnorm40.frame)

cfunc <- function(x, n) sqrt(n) * (mean(x) - (mean) ) / (sd)
dat <- tbl_df(data.frame(
    x = c(apply(rnorm30.frame, 1, cfunc, 30),
          apply(rnorm40.frame, 1, cfunc, 40),
          apply(rnorm50.frame, 1, cfunc, 50)
    ),
    size = factor(rep(c("30 Students", "40 Students", "50 Students"), rep(1000, 3)))))
#     size = factor(rep(c("30 Students", "40 Students", "50 Students"), rep(1000, 3)))))
# View(dat)
pltLLNnorm <- ggplot(dat, aes(x = x, fill = size)) + geom_histogram(binwidth=.3, colour = "black", aes(y = ..density..)) 
pltLLNnorm <- pltLLNnorm + stat_function(fun = dnorm, size = 2) + 
    labs(y = "Density", title = "Central Limit Theorem:  Normal Distribution")
pltLLNnorm <- pltLLNnorm + facet_grid(. ~ size)

grid.newpage()
pushViewport(viewport(layout = grid.layout(1, 2)))
vplayout <- function(x, y)
    viewport(layout.pos.row = x, layout.pos.col = y)
print(plotHistRnorm, vp = vplayout(1, 1))
print(pltLLNnorm, vp = vplayout(1, 2))

```
* figure courtesy of Dr McDougall

---
## Tools from Stochastic Calculus

### Ito's Lemma
* Show definition of Ito's lemma


---
## Definitions from Finance

### Stock
* An asset that is partial ownership of a publicly traded firm.


### European Option
* Right to buy (long) or sell (short) an asset (stock) at a strike price at a fixed date (maturity), for a fee today.


### Call Option
* The option to buy a stock in the future at a fixed price.
* Two sides:  buyer and seller

### Put Option
* The option to sell a stock in the future at a fixed price.
* Two sides:  buyer and seller


---

## Future Value of Money

r = risk free interest rate   
PV = Present Value of Money  
FV = Future Value of Money
$$ FV_1 = PV + r(PV) $$

---

## Future Value of Money


r = risk free interest rate   
PV = Present Value of Money  
FV = Future Value of Money
$$ FV_1 = PV + r(PV) $$
  
### Example:
$$ r = 10\% $$
$$ PV = $100 $$
$$ FV_1 = ? $$

---

## Future Value of Money

r = risk free interest rate   
PV = Present Value of Money  
FV = Future Value of Money
$$ FV_1 = PV + r(PV) $$
  
### Example:
$$ FV_1 = $100 + (10\%)($100) $$
$$ FV_1 = $110 $$

---

## Future Value of Money

r = risk free interest rate   
PV = Present Value of Money  
FV = Future Value of Money
$$ FV_1 = PV + r(PV) $$

---

## Future Value of Money


r = risk free interest rate   
PV = Present Value of Money  
FV = Future Value of Money
$$ FV_1 = PV + r(PV) $$


$$ FV_2 = (FV_1) + r(FV_1) $$

---

## Future Value of Money

r = risk free interest rate   
PV = Present Value of Money  
FV = Future Value of Money
$$ FV_1 = PV + r(PV) $$

$$ FV_2 = (FV_1) + r(FV_1) $$

$$ FV_2 = (PV + r(PV)) + r(PV + r(PV)) $$

---

## Future Value of Money

r = risk free interest rate   
PV = Present Value of Money  
FV = Future Value of Money
$$ FV_1 = PV + r(PV) $$

$$ FV_2 = (FV_1) + r(FV_1) $$


$$ FV_2 = (PV + r(PV)) + r(PV + r(PV)) $$






$$ FV_2 = PV(1 + 2r + r^2) $$




$$ FV_2 = PV(1+r)^2 $$

---

## Future Value of Money

r = risk free interest rate   
PV = Present Value of Money  
FV = Future Value of Money
$$ FV_1 = PV + r(PV) $$



$$ FV_2 = PV(1+r)^2 $$

$$ FV_t = PV(1+r)^t $$




$$ FV_t = PV(1+\frac{r}{n})^{nt} $$


### -t is a time step
### -n is a unit conversion

---

## Future Value of Money

r = risk free interest rate   
PV = Present Value of Money  
FV = Future Value of Money  
n = Unit Conversion  
t = Time Conversion

$$ FV_t = PV(1+\frac{r}{n})^{nt} $$

$$ k = \frac{n}{r} $$

$$ n = k*r $$


$$ FV_t = PV(1+\frac{1}{k})^{krt} $$

---

## Future Value of Money
r = risk free interest rate   
PV = Present Value of Money  
FV = Future Value of Money  

$$  e = \lim_{x\to\infty} (1+\frac{1}{x})^x $$

$$ FV_t = PV(\lim_{k\to\infty} (1+\frac{1}{k})^{k})^{rt} $$

$$ FV_t = PV (e^{rt}) $$

---
## Future Value of Money

* [Bank Savings interest rate](http://www.mysavingsdirect.com/MySavingsDirectWeb/en/common/information/LearnMore.jsp) $r = 1.25\%$ per annum. Starting balance = [$532.60](http://www.google.com/finance?q=NASDAQ%3AGOOGL&ei=fsF9VfG5JonSjAGE84J4)
* Figure shows continuous, daily, monthly, quarterly, and annual compounding for 10 years
```{r fvMoney, echo=FALSE, warning=FALSE, message=FALSE, fig.height=5, fig.width=12, fig.cap="Time Value of Money"}
aprAnn = 0.0125 #https://www.mysavingsdirect.com/MySavingsDirectWeb/en/common/information/LearnMore.jsp
aprDay = aprAnn / yday(mdy("12/31/2015"))
aprMnth = aprAnn / 12
aprQtr = aprAnn / 4

finGrowthTblMnth <- tbl_df(as.data.frame( ymd_hms("2015-01-01 16:00:00", tz = "America/New_York") + months(1:120) - days(1) ))
names(finGrowthTblMnth) <- "dateClose"
finGrowthTblMnth <- finGrowthTblMnth%>%
    mutate(
        ydayNum = yday(dateClose),
        month = month(dateClose),
        years = as.period( (dateClose - ymd_hms("2015-01-02 16:00:00", tz = "America/New_York") ) ) %/% months(12),
        quarters = as.period( (dateClose - ymd_hms("2015-01-02 16:00:00", tz = "America/New_York") ) ) %/% months(3),
        months = as.period( (dateClose - ymd_hms("2015-01-02 16:00:00", tz = "America/New_York") ) ) %/% months(1),
        days = as.period( (dateClose - ymd_hms("2015-01-02 16:00:00", tz = "America/New_York") ) ) %/% days(1),
        Savings = (532.60 * (1 + aprDay)**(days)),
        Contin = (532.60 * exp( aprDay * days) ),
        Mnthly = (532.60 * (1 + aprMnth)**(months)),
        Qtrly = (532.60 * (1 + aprQtr)**(quarters)),
        Annul = (532.60 * (1 + aprAnn)**(years))
        )
    
mnyPlt2 <- ggplot() + scale_colour_hue("Compound_Rate")
mnyPlt2 <- mnyPlt2 + geom_line(data=finGrowthTblMnth, aes(x = dateClose, y = Contin, color = "1_Contin"))
mnyPlt2 <- mnyPlt2 + geom_line(data=finGrowthTblMnth, aes(x = dateClose, y = Savings, color = "2_Daily"))
mnyPlt2 <- mnyPlt2 + geom_line(data=finGrowthTblMnth, aes(x = dateClose, y = Mnthly, color = "3_Mnthly"))
mnyPlt2 <- mnyPlt2 + geom_line(data=finGrowthTblMnth, aes(x = dateClose, y = Qtrly, color = "4_Qtrly"))
mnyPlt2 <- mnyPlt2 + geom_line(data=finGrowthTblMnth, aes(x = dateClose, y = Annul, color = "5_Annul"))
mnyPlt2 <- mnyPlt2 + labs(x = "Date", y = "Amount [$]", title = "Money:  Time Value", legend = "Compounding")
mnyPlt2
```
* Speculation: bank income is area between continuous compounding curve and client's compounding curve
* figure courtesy of Dr McDougall

---
## Risk Neutral Valuation of a Portfolio

### Assumptions
1. Expected return on a stock (or any other instrument) is the risk-free rate $e^{rt}$.
2. Discount rate for payoff on an option (or any other instrument) is the risk-free rate $e^{-rt}$.

### Purpose
1. Risk Neutral Valuation (RNV) simplifies pricing.

* All returns and discounts are at risk-free rate.

2. **Relationship between stock and derivative is the same regardless of risk**.

* Risk incorporated into price of stock.

---

## Portfolio Management (1 / 4)

### Generate RNV Portfolio using [Binary Tree Model](https://en.wikipedia.org/wiki/Binomial_options_pricing_model)
1. Purchasing $\Delta$ shares of stock at price $S_o$
2. Short a call option on same stock with value $f$

* Value of RNV portfolio is same whether stock price goes up or down

\begin{equation}
    (\Delta S_o) u - f_u = (\Delta S_o) d - f_d
\end{equation}
where u is the multiplier  for increase and d is multiplier for decrease

### $\Delta$ Hedge for RNV Portfolio
* From equality, $\Delta$ required for creating a RNV Portfolio is

\begin{equation}
    \Delta = \frac{f_u - f_d}{S_o (u-d)}
\end{equation}

---
## Portfolio Management (2 / 4)

### The figure depicts a RNV portfolio generated from Binary Tree Model
* figure courtesy of Dr McDougall

```{r echo=FALSE, warning=FALSE,cache=FALSE,results='asis'}
# <style type="text/css">
#     body {background:none transparent;
#           }
# </style>

fff <- DiagrammeR::grViz("
                        digraph {
                        
                        # graph attributes
                        graph [overlap = true]
                        
                        # node attributes
                        node [shape = box,
                        fontname = Helvetica,
                        color = blue]
                        
                        # edge attributes
                        edge [color = gray]
                        
                        # node statements
                        A; B; C; D; E; F
                        
                        A [ label = 'S_o \n f']
                        B [ label = 'd S_o \n f_d']
                        C [ label = 'u S_o \n f_u']
                        D [ label = 'd d S_o \n f_dd']
                        E [ label = 'u d S_o \n f_ud']
                        F [ label = 'u u S_o \n f_uu']
                        
                        #   # node attributes
                        #   node [shape = circle,
                        #         fixedsize = true,
                        #         width = 0.9]
                        # 
                        #   # node statements
                        #   1; 2; 3; 4; 5; 6; 7; 8
                        # 
                        #   # edge statements
                        A->B; A->C
                        B->D; B->E
                        C->F; C->E
                        #   A->1; B->2                   // gray
                        #   B->3 [color = red]           // red
                        #   B->4                         // gray
                        #   C->A [color = green]         // green
                        #   1->D; E->A; 2->4; 1->5; 1->F // gray
                        #   E->6; 4->6; 5->7; 6->7       // gray
                        #   3->8 [color = blue]          // blue
                        }
                        ", width=800, height=350, engine="dot")

saveWidget(fff, 'diagram.html')
cat('<iframe src="diagram.html" width=100% height=100% allowtransparency="true"> </iframe>')
```


---
## Portfolio Management (3 / 4)

* PV of RNV is discounted FV, i.e.

<div class="centered">
\begin{equation}
    (\Delta S_o)  - f = e^{-r t} \left[ (\Delta S_o) u - f_u \right]
\end{equation}
</div>

* Solving for f estimates PV of call option, so
\begin{equation}
\vdots
\end{equation}

<div class="centered">
\begin{equation}
   f = e^{-r t} \left[ p f_u + (1 - p) f_d \right]
\end{equation}
</div>
where
<div class="centered">
\begin{equation}
   p = \frac{e^{r t} - d}{u - d}
\end{equation}
</div>

* **NOTE**:  f is discounted expectation value of option's FV with a binomial density (*coin flip*)

---
## Portfolio Management (4 / 4)

### From Probability Theory, variance is proportional to $\Delta t$, so

<div class="centered">
\begin{equation}
    \sigma^2 \Delta t = \langle S(t)^2 \rangle - \langle S(t) \rangle ^2
\end{equation}
</div>

\begin{equation}
\vdots
\end{equation}

<div class="centered">
\begin{equation}
   \sigma^2 \Delta t = \left[ p u^2 + (1-p) d^2 \right] - \left[ \left( p u + (1-p) d \right)^2 \right]
\end{equation}
</div>

\begin{equation}
\vdots
\end{equation}


<div class="centered">
\begin{equation}
   \sigma^2 \Delta t = (u + d) e^{\mu t} - du - e^{2 \mu t}
\end{equation}
</div>

* with a Taylor Expansion, one validates a solution for u & d is $u = e^{\sigma \sqrt{\Delta t}}$ & $d = e^{- \sigma \sqrt{\Delta t}}$



---
## Pricing a Stock

### Current Status
* Given a RNV Portfolio, binary tree model prices a call option for a $\Delta$ Hedge
* The binary tree model is transformed from *RNV world* to *market world* by incorporating market return $\mu$ and volatility $\sigma^2 \Delta t$ in price multipliers $u$ & $d$
* Remaining action is determining time dependence of stock price $S$
* Two necessary properties are:

1.  The change $\Delta z$ during a small period of time $\Delta t$ is $\Delta z = \epsilon \sqrt(\Delta t)$ where $\epsilon$ is a standard normal distribution.
2.  The values of $\Delta z$ for any two different short intervals of time, $\Delta t$, are independent.

---
## Time Dependence of Stock Price $S$

<div class="centered">
\begin{equation}
    d S = \mu S d t + \sigma S \epsilon \sqrt{dt}
\end{equation}
</div>

* Neglecting volatility, $S(t) = S_o e^{\mu t}$
* Solving numerically,
\begin{equation}
\vdots
\end{equation}

<div class="centered">
\begin{equation}
     \Delta S = \mu S \Delta t + \sigma S \epsilon \sqrt{\Delta t}
\end{equation}
</div>

\begin{equation}
\vdots
\end{equation}


<div class="centered">
\begin{equation}
    S_{i + 1} = S_i + \mu S_i \Delta t + \sigma S_i \epsilon \sqrt{\Delta t}
\end{equation}
</div>


---
## Google vs Savings Account
### Numerical approximation to Google's stock price (Dates:  1/2/2015 - 6/12/2015)
```{r stockPricing, echo=FALSE, message=FALSE, warning=FALSE, fig.height=6, fig.width=12, fig.show='animate'}
################################################################################
##
## This section is for comparing Google Stock Price with Wiener Pricing of Stock
##  For comparison, bank savings is shown.  Import Google price history. 
##
finGrowthTbl <- tbl_df(
    read.csv2("googl.csv", sep = ",", stringsAsFactors = FALSE, na.strings = "NA",
              header = TRUE, #colClasses = c("character", "numeric", "numeric", "numeric", "numeric", "numeric")
              )
    )   %>%
    select(
        Date, Open, High, Low, Close, Volume
        ) %>%
    mutate(
        dateClose = ymd_hms( paste( dmy(Date), hms(c("16:00:00") )), tz = "America/New_York"),
        Open = as.numeric(Open), High = as.numeric(High), Low = as.numeric(Low), Close = as.numeric(Close),
        Volume = as.numeric(Volume)
        ) %>%
    select(
        dateClose,
        Date, Open, High, Low, Close, Volume      
        )  %>%
    filter(
        dateClose > mdy("01/01/2015") & dateClose < mdy("06/30/2015")
        ) %>%
    mutate(
        ydayNum = yday(dateClose),
        days = as.period( (dateClose - ymd_hms("2015-01-02 16:00:00", tz = "America/New_York") ) ) %/% days(1)        
        )%>%
    arrange(ydayNum)%>%
    mutate(
        Savings = (532.60 * (1 + aprDay)**(days)),
        Contin = (532.60 * exp( aprDay * days) ),
        goog_W = 0
        )%>%
    select(
        dateClose, days,
        Open, High, Low, Close, goog_W, Savings
        )
##
################################################################################
##
## This section for determining volatility in Google Stock between 2015-01-02
##  and 2015-06-12, which is 112 trading days and estimate Stock price with Wiener model
##
sd_googl <- sd(finGrowthTbl$Close) # for 112 trading days
sd_googlDly <-  sd_googl / 112
mu <- (547.47 - 532.60) / 532.60 # ~0.15 annualized rate of return from
# https://www.stock-analysis-on.net/NASDAQ/Company/Google-Inc/Valuation/Ratios
mu_daily <- mu / 112

goog_W <- vector("numeric", length = 112)
goog_W[1] <- 532.60

for(j in 1:30) {
    count <- count + 1
    for(i in 2:112) {
        #     set.seed(314159)
        goog_W[i] <- goog_W[i-1] * (1 + mu_daily * (1/365) + sd_googlDly * rnorm(1) * sqrt(1/365)) 
    }
    finGrowthTbl$goog_W <- goog_W
    
    mnyPlt <- ggplot() + scale_colour_hue("Instrument") + scale_y_continuous(limits = c(450, 650))
    mnyPlt <- mnyPlt + geom_line(data=finGrowthTbl, aes(x = dateClose, y = Close, color="GOOGL"))
    mnyPlt <- mnyPlt + geom_line(data=finGrowthTbl, aes(x = dateClose, y = goog_W, color="goog_W"))
    mnyPlt <- mnyPlt + geom_line(data=finGrowthTbl, aes(x = dateClose, y = Savings, color = "Savings"))
    mnyPlt <- mnyPlt + labs(x = "Date", y = "Amount [$]", title = "Money:  Time Value")
    print(mnyPlt)
}
```
* Animation provided by Dr McDougall

---
## Conclusions

### Finance utilizes multiple branches of mathematics
* from Algebra to Stochastic Calculus

### Future value of our money depends on $r$ and short compounding intervals

### $\Delta$ Hedging demonstrates earning income at market rate $\mu$ with negligible risk
* ratio between Google's rate of return and best available bank rate is $\mu / r =$ ```r round(mu_daily / aprDay, 2)```
* high frquency trading rate is of order $1 \mu s$ vs daily, $\ldots$, or annual compounding of banks

### Binary Tree approximation enables pricing of call option for $\Delta$ Hedging.

### Binary Tree approximation with Wiener Process enables estimation of stock price
* Wiener process shows risk of stochastic processes in pricing model
* $\Delta$ Hedging mitigates inherent risk due of stochastic processes

---
## Acknowledgements

### Ms Johnston
* for AP Calculus

### Dr McDougall

* for stimulating discussions regarding Cox, Ross, Rubinstein model,
* introducing a R-programming enviroment, 
* demonstrating Latex,
* introducing GitHub, and
* keeping us at the white board!

### References
* Hull, J.C., **Options, Futures, And Other Derivatives**, 8th ed., Pearson Education Limited, England (2012)

