---
title       : Brief Introduction to Pricing Derivatives
subtitle    : Pricing a Call Option with a Two Step Binomial Model
author      : Robby Twesten & Tristan McDougall 
job         : RT Financials
framework   : io2012     # {io2012, html5slides, shower, dzslides, ...}
highlighter : highlight.js  # {highlight.js, prettify, highlight}
hitheme     : tomorrow      # 
widgets     : [mathjax, bootstrap]            # {mathjax, quiz, bootstrap}
mode        : selfcontained # {standalone, draft}
knit        : slidify::knit2slides
---

## Basics

### Tools:  
1. Programming Environment
2. Probability
3. Algebra
4. Calculus

### Finance Theory:  
1. Future Value of Money
2. Binomial Tree Pricing Model for Option


--- .class #id

## Definitions

### Stochastic Process
#### An observation whose value is random with respect to time.

### Option
#### The rights to buy an asset for a set price at a set time, for a small fee today.

### Call Option
#### Selling an option.

---

## Future Value of Money

r = rate / time   
Pv = Present Value of Money  
Fv = Future Value of Money
$$ Fv_1 = Pv + r(Pv) $$

---

## Future Value of Money

r = rate / time   
Pv = Present Value of Money  
Fv = Future Value of Money
$$ Fv_1 = Pv + r(Pv) $$
  
### Example:
$$ r = 10\% $$
$$ Pv = $100 $$
$$ Fv_1 = ? $$

---

## Future Value of Money

r = rate / time   
Pv = Present Value of Money  
Fv = Future Value of Money
$$ Fv_1 = Pv + r(Pv) $$
  
### Example:
$$ Fv_1 = $100 + (10\%)($100) $$
$$ Fv_1 = $110 $$

---

## Future Value of Money

r = rate / time   
Pv = Present Value of Money  
Fv = Future Value of Money
$$ Fv_1 = Pv + r(Pv) $$

---

## Future Value of Money

r = rate / time   
Pv = Present Value of Money  
Fv = Future Value of Money
$$ Fv_1 = Pv + r(Pv) $$

$$ Fv_2 = (Fv_1) + r(Fv_1) $$

---

## Future Value of Money

r = rate / time   
Pv = Present Value of Money  
Fv = Future Value of Money
$$ Fv_1 = Pv + r(Pv) $$

$$ Fv_2 = (Fv_1) + r(Fv_1) $$

$$ Fv_2 = (Pv + r(Pv)) + r(Pv + r(Pv)) $$

---

## Future Value of Money

r = rate / time   
Pv = Present Value of Money  
Fv = Future Value of Money
$$ Fv_1 = Pv + r(Pv) $$

$$ Fv_2 = (Fv_1) + r(Fv_1) $$

$$ Fv_2 = (Pv + r(Pv)) + r(Pv + r(Pv)) $$

$$ Fv_2 = Pv(1 + 2r + r^2) $$

$$ Fv_2 = Pv(1+r)^2 $$

---

## Future Value of Money

r = rate / time   
Pv = Present Value of Money  
Fv = Future Value of Money
$$ Fv_1 = Pv + r(Pv) $$

$$ Fv_2 = Pv(1+r)^2 $$

$$ Fv_t = Pv(1+r)^t $$

$$ Fv_t = Pv(1+\frac{r}{n})^{nt} $$

### -t is a time step
### -n is a unit conversion

---

## Future Value of Money

r = rate / time   
Pv = Present Value of Money  
Fv = Future Value of Money  
n = Unit Conversion  
t = Time Conversion

$$ Fv_t = Pv(1+\frac{r}{n})^{nt} $$

$$ k = \frac{n}{r} $$

$$ n = k*r $$

$$ Fv_t = Pv(1+\frac{1}{k})^{krt} $$

---

## Future Value of Money
r = rate / time   
Pv = Present Value of Money  
Fv = Future Value of Money  

$$  e = \lim_{x\to\infty} (1+\frac{1}{x})^x $$

$$ Fv_t = Pv(\lim_{k\to\infty} (1+\frac{1}{k})^{k})^{rt} $$

$$ Fv_t = Pv (e^{rt}) $$

---

## Binomial Tree Model
  
  
The Binomial Tree Pricing Model demonstrates options pricing in one discrete time step.

### Risk Neutral Valuation

1. Creates a risk free portfolio for both the buyer and the seller
2. Greatly simplifies pricing

### Assumptions

1. Value of the portfolio is the same whether the stock price goes up or down.
2. The expected return on a stock (or any other investment) is the risk-free rate.

---

## Binomial Tree Model
  
  
$S_0 =$ Initial stock Price  
  
$u =$ Multiplier when stock price goes up  
  
$d =$ Multiplier when stock price goes down  
  
$f =$ Value of the option  
  
$f_u =$ Value of the option when stock price goes up  
  
$f_d =$ Value of the option when stock price goes down  
  
$\Delta =$ Number of shares in portfolio  

---

## Binomial Tree Model (Example)  
  
  
  
$f$ is the option to buy stock for $21  
  
$S_0 = 20$  
  
$uS_0 = 22$   
  
$dS_0 = 18$  

$f_u = 22-21 = 1$    
  
$f_d = 0$   


---

## Binomial Tree Model
### Hedging
   
   - The elimination of risk.  
   
1. To do this in our model we determine a number of shares, $\Delta$, that would make the value of the portfolio if the stock goes down equal to the value of the portfolio if the stock goes up.
   
2.In our example this is done by setting $\Delta 22 - 1 =  \Delta 18$  

---

## Integrated Development Environment (IDE)

### R:
* Open Source Code & Shared Libraries
```{r echo=FALSE, warning=FALSE, results='hide', message=FALSE}
require(stringr)
require(slidify)
require(knitr)
require(DiagrammeR)
```
* Plotting, Typesetting, & Slide Presentations

### Version Control
 1. [Git](https://www.git-scm.com) invented by Linus Torvalds (open source Linux)
 2. [Git Hub](https://github.com/RobertTwesten/Tristan) distributed version control ([used by Google](https://github.com/google))
 
---



---



---
## Tools from Probability

### Binomial Distribution
1. $E[X] = n p$
2. $Var(X) = n p(1 - p)$

---
## Risk Neutral Valuation

### Assumptions
1. The expected return on a stock (or any other investment) is the risk-free rate.
2. The discount rate used for the expected payoff on an option (or any other instrument) is the risk-free rate.

### Purpose
1. Risk Neutral Valuation (RNV) simplifies pricing.

All returns and discounts are at risk-free rate.

2. Relationship between stock and derivative is the same regardless of risk.

Risk incorporated into price of stock.

---
## Risk Free Portfolio (RFP)

### Value of portfolio is same whether stock price goes up or down:

\begin{equation}
    (\Delta S_o) u - f_u = (\Delta S_o) d - f_d
\end{equation}

### $\Delta$ Hedge
### Determine number of shares required for RFP

\begin{equation}
    \Delta = \frac{f_u - f_d}{S_o (u-d)}
\end{equation}

---

## Stochastic Processes

### Stochastic processes are observations whose value is random with respect to time.

### Markov Process
* Markov process with respect to stock price implies that future price only depends on current price.
* Distribution is normal

Means are additive and variances are additive

---

## Wiener Process
* Distribution is standard normal, i.e. mean = 0 and variance = 1.

A physical example of a Wiener processes is Brownian motion.

$Var(X) = E[X^2] - (E[X])^2$

* Two properties are:
1.  The change $\Delta z$ during a small period of time $\Delta t$ is $\Delta z = \epsilon \sqrt(\Delta t)$ where $\epsilon$ is a standard normal distribution $\Phi(0,1)$.
2.  The values of $\Delta z$ for any two different short intervals of time, $\Delta t$, are independent.

---

```{r robby}
1+1
```
a different test
```{r tristan}
2*2
```


